---
title: "Modality effects in a signalling game: Accuracy"
output:
    pdf_document:
        toc: true
        includes:
            in_header: header.tex 
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), "../../results/MainResults_Accuracy.pdf")) })
---

# Intro 

This script uses data compiled by *analyseData.R*.

## Load libraries

```{r warning=FALSE, message=FALSE}
library(lme4)
library(sjPlot)
library(ggplot2)
library(lattice)
library(influence.ME)
library(party)
library(dplyr)
```

```{r echo=F}
try(setwd("~/Documents/MPI/ViniciusMultimodal/multimodalCommunicationGame/experiment/analysis/R/"))
```

## Load data

```{r}
d = read.csv("../../data/FinalSignalData.csv")
```

Work out number of turns in each trial.

```{r}
# Number of turns in each trial
numTurns = tapply(d$turnString, d$trialString, 
                  function(X){length(unique(X))})
d$numberOfTurns = numTurns[d$trialString]
```

Variable for length of first T1

```{r}
T1L = tapply(d[d$turnType=="T1",]$turnLength,
             d[d$turnType=="T1",]$trialString, head, n=1)
d$T1Length = T1L[d$trialString]
d$T1Length[is.na(d$T1Length)] = mean(d$T1Length,na.rm=T)
d$T1Length.log = log(d$T1Length)
d$T1Length.log = d$T1Length.log - mean(d$T1Length.log)
```

Did matcher respond?

```{r}
matcherResponds = tapply(d$turnType, d$trialString, function(X){
  any(X %in% c("T2","T4","T6","T8",'T10'))
})
d$matcherResponds = matcherResponds[d$trialString]
```

We don't need info on every signal in each turn, just the trial time.  Keep only 1st signal in each trial.

```{r}
d = d[!duplicated(d$trialString),]
```



# Descriptive stats

Here is a graph showing the distribution of accuracy by conditions:

```{r}
summary = d %>% 
  group_by(condition, modalityCondition,game) %>% 
  summarise(Accuracy=mean(correct),
            sd=sd(correct),
            ci.w =           qnorm(0.95)*sd/sqrt(length(correct)),
            upper=Accuracy+ci.w,
            lower = Accuracy-ci.w)
summary$game = summary$game +1

summary$modalityCondition =
  factor(summary$modalityCondition,
         levels = c("visual",'multi','vocal'),
         labels=c("Gestural","Multimodal","Vocal"))

#ggplot(d, aes(x=trialTotal, y=as.numeric(correct),colour=modalityCondition)) +
#  geom_smooth() + facet_grid(.~condition)

#ggplot(d, aes(x=trialTotal, y=as.numeric(correct),colour=condition)) +
#  geom_smooth() + #facet_grid(.~modalityCondition)

ggplot(summary, aes(x=game, y=Accuracy, group=condition, colour=modalityCondition)) + 
  geom_point() +
  geom_errorbar(aes(ymin=lower, ymax=upper)) +
  facet_grid(. ~ condition) +
  stat_summary(fun.y="mean", geom="line", aes(group=modalityCondition))

gx = ggplot(summary, aes(x=game, y=Accuracy, group=condition, colour=condition, shape=condition)) + 
  geom_point() +
  geom_errorbar(aes(ymin=lower, ymax=upper)) +
  facet_grid(. ~ modalityCondition) +
  stat_summary(fun.y="mean", geom="line", aes(group=condition)) +
  scale_colour_brewer(palette="Dark2",name="Stimuli") +
  scale_shape_discrete(name="Stimuli") +
  xlab("Game")
gx
pdf("../../results/graphs/Accuracy_gg.pdf",
    width = 5, height=3)
gx
dev.off()

pd = position_dodge(width=0.5)
gx1 = ggplot(summary, aes(x=game, y=Accuracy, group=condition, colour=modalityCondition)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper,group=modalityCondition), width=0.5,position = pd) +
  stat_summary(fun.y="mean", geom="line", aes(group=modalityCondition),position = pd) +
  geom_point(aes(group=modalityCondition,shape=modalityCondition),position=pd) +
  scale_colour_brewer(palette="Set2", name="Condition") +
  scale_shape(name="Condition") +
  ggtitle("Accuracy") +
  theme(panel.grid.major.x = element_blank()) +
  facet_grid(. ~ condition) +
  xlab("Game")

gx1
pdf("../../results/graphs/Accuracy_gg_alt.pdf",
    width = 5, height=3)
gx1
dev.off()
```

\newpage

Make a variable to represent proportion of games played:

```{r}
# Make a variable that represents the number of trials played
d$trialTotal = d$trial + (d$game * (max(d$trial)+1))
# Convert to proportion of games played, so that estimates reflect change per game.
d$trialTotal = d$trialTotal / 16
# Center the trialTotal variable so intercept reflects after the first game
d$trialTotal = d$trialTotal

```

Average accuracy per dyad:

```{r}
av.acc = tapply(d$correct, d$dyadNumber, function(X){sum(X)/length(X)})
mean(av.acc)
```



Make a variable for which stimuli the players experienced first.

```{r}
firstBlock = tapply(as.character(d$condition),d$dyadNumber,head,n=1)
d$firstBlock = as.factor(firstBlock[match(d$dyadNumber,names(firstBlock))])
```

Variable to indicate whether T1 is multimodal.

```{r}
turnD = read.csv("../../data/Final_Turn_data.csv")
turnD = turnD[turnD$turnType=="T1",]
turnD = turnD[turnD$role == "Director",]
d$multimodal = turnD[match(d$trialString, turnD$trialString),]$turnModalityType == "multi"
d$multimodal[is.na(d$multimodal)] = F
```

Make a variable to represent proportion of games played:

```{r}
# Make a variable that represents the number of trials played
d$trialTotal = d$trial + (d$game * (max(d$trial)+1))
# Convert to proportion of games played, so that estimates reflect change per game.
d$trialTotal = d$trialTotal / 16
# Center the trialTotal variable so intercept reflects after the first game
d$trialTotal = d$trialTotal - 2
```

Transformed trial time.

```{r}
d$trialLength.log = log(d$trialLength)
meanLogTrialLength = mean(d$trialLength.log)
d$trialLength.log = d$trialLength.log - meanLogTrialLength 
```


Get an idea of the structure of the data from a binary tree:
```{r}
cx = ctree(correct ~ modalityCondition + condition +
            trialTotal +
            trialLength +
            matcherResponds +
            matcherResponds +
            T1Length +
            multimodal+
            firstBlock,
          data=d)
```
\blandscape
```{r fig.width=20, fig.height=8}
plot(cx, terminal_panel=node_barplot(cx))
```
\elandscape


\newpage

# Mixed models

There are celing effects in the data, which reduces variance and makes model convergence difficult.  Experimentation revealed that random effects other than random intercepts for dyad and item lead to non-convergence.

The final models do not converge within standard tolerances, but the convergence is acceptable.

```{r models, cache=TRUE}
# No fixed effects

gc = glmerControl(optimizer = "bobyqa" ,optCtrl = list(maxfun=50000))

m0 =  glmer(correct ~ 1 +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

game = glmer(correct ~ 1 + 
            trialTotal +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

trialL = glmer(correct ~ 1 +
            trialTotal +
            trialLength.log+
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

t1L = glmer(correct ~ 1 + 
            trialTotal +
            trialLength.log +
            T1Length.log +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

multi = glmer(correct ~ 1 +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)


mtchTrn = glmer(correct ~ 1 +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            matcherResponds +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

tMtchTr = glmer(correct ~ 1 +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

con = glmer(correct ~ 1 + condition +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

mod = glmer(correct ~ 1 + modalityCondition + condition +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

modXcon = glmer(correct ~ 1 + modalityCondition * condition +
            trialTotal +
            trialLength.log +
            T1Length.log +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

trialLXmo = glmer(correct ~ 1 + modalityCondition * condition +
            trialTotal +
            trialLength.log * modalityCondition+
            T1Length.log +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

t1LXmo = glmer(correct ~ 1 + modalityCondition * condition +
            trialTotal +
            trialLength.log * modalityCondition+
            T1Length.log *modalityCondition +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

tMaTXmo = glmer(correct ~ 1 + modalityCondition * condition +
            trialTotal +
            trialLength.log * modalityCondition+
            T1Length.log *modalityCondition +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
              matcherResponds.cumulative:modalityCondition +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)


block = glmer(correct ~ 1 + modalityCondition * condition +
            trialTotal +
            trialLength.log * modalityCondition+
            T1Length.log *modalityCondition +
            multimodal+
            matcherResponds +
            matcherResponds.cumulative +
              matcherResponds.cumulative:modalityCondition +
            matcherResponds +
            firstBlock +
            (1 + condition |dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)

```

\newpage

# Results

Compare the fit of the models:

```{r anova}
modelComparison = anova(m0,con,mod,modXcon, 
                        game, trialL,trialLXmo,
                        t1L, t1LXmo, mtchTrn, tMtchTr,tMaTXmo,
                        multi, block)
x = capture.output(modelComparison)
x[!grepl(": ",x)]
```

Final model with only significant variables:

```{r}
finalModel = glmer(correct ~ 1 + 
            modalityCondition * condition +
            trialTotal +
            trialLength.log +
            matcherResponds.cumulative +
            (1 + condition | dyadNumber/playerId) +
            (1 + modalityCondition |itemId) ,
          data=d, family=binomial,
          control = gc)
```

Model estimates:

```{r}
summary(finalModel)
# number of correctly categorised trials
sum((predict(finalModel)>0) == d$correct)/nrow(d)
```

Surprisingly, the interaction between modality and stimulus condition is not significant. In comparison, in a model without random slopes, the interaction is significant:

```{r}
finalModel.simple = glmer(correct ~ 1 + 
            modalityCondition * condition +
            trialTotal +
            trialLength.log +
            matcherResponds.cumulative +
            (1  |dyadNumber/playerId) +
            (1  |itemId) ,
          data=d, family=binomial,
          control = gc)
summary(finalModel.simple)
```

By model comparison, we should prefer the model with random slopes:

```{r}
anova(finalModel.simple,finalModel)
```

This suggests that, while accuracy is lower for visual stimuli in the vocal condition, the difference is not greater than might be expected by random (slope) variation between dyads and items.

We also show that a model with more random slopes is essentially identical to the simpler random slopes model:

```{r cache=T}
finalModel.full = glmer(correct ~ 1 + 
            modalityCondition * condition +
            trialTotal +
            trialLength.log +
            matcherResponds.cumulative +
            (1 + condition + trialTotal + trialLength.log + 
               matcherResponds.cumulative |dyadNumber/playerId) +
            (1 + modalityCondition + trialTotal + trialLength.log + 
               matcherResponds.cumulative |itemId) ,
          data=d, family=binomial,
          control = gc)
cor(fixef(finalModel.full),fixef(finalModel))
```


## Plot the fixed effects

Relabel the effects:

```{r}

feLabels = matrix(c(
"(Intercept)"             ,"Intercept"      , NA,                         
"modalityConditionvisual" ,"Visual modality", "mod",
"modalityConditionvocal"  , "Acoustic modality", "mod",
"conditionVisual" , "Visual stimuli","con",
"trialTotal"             , "Game","game",
"modalityConditionvisual:conditionVisual"  , "Visual modality:Visual stimuli", "modXcon",
"modalityConditionvocal:conditionVisual" , "Acoustic modality:Visual stimuli","modXcon",
"firstBlockVisual","Visual stims first","block",
"trialLength.log","Trial length","trialL",
"modalityConditionvisual:trialLength.log","Visual modality:Trial length",'trialLXmo',
"modalityConditionvocal:trialLength.log","Acoustic modality:Trial length",'trialLXmo',
"multimodalTRUE","Multimodal T1","multi",
"trialLength.log",'Trial Length','trialL',
"T1Length.log","T1 length","t1L",
"modalityConditionvisual:T1Length.log","T1 length:Visual modality","t1LXmo",
"modalityConditionvocal:T1Length.log","T1 length:Acoustic modality","t1LXmo",
"matcherRespondsTRUE","Matcher Responds",'mtchTrn',
"matcherResponds.cumulative","Total interaction","tMtchTr",
"modalityConditionvisual:matcherResponds.cumulative","Total interaction:Visual Modality","tMaTXmo",
"modalityConditionvocal:matcherResponds.cumulative","Total interaction:Vocal Modality","tMaTXmo"
), ncol=3, byrow = T)
feLabels1 = as.vector(feLabels[match(names(fixef(finalModel)),feLabels[,1]),1])
feLabels2 = as.vector(feLabels[match(names(fixef(finalModel)),feLabels[,1]),2])
feModel = as.vector(feLabels[match(names(fixef(finalModel)),feLabels[,1]),3])

sig = modelComparison$`Pr(>Chisq)`
names(sig) = rownames(modelComparison)

sig.data = data.frame(
  estimate = fixef(finalModel),
  y=1:length(fixef(finalModel)),
  sig=sig[feModel])
sig.data$fade = sig.data$sig > 0.05
```

Plot the strength of the fixed effects:


```{r}
plot_model(finalModel, 'est', 
         show.intercept = T,
         sort.est=NULL,
         axis.labels = feLabels2[2:length(feLabels2)],
         axis.title="Odds of correct selection",
         colors = c(1,1),
         show.values = F,
         show.p = T,
         string.interc="Intercept",
         prnt.plot = F) 
```

Table of results

```{r}
x = as.data.frame(summary(finalModel)$coef)
mc = as.data.frame(modelComparison)
finalRes= cbind(x,mc[feModel,])
write.csv(finalRes, "../../results/tables/Accuracy_FixedEffects.csv")
```


\newpage

## Random effects

```{r}
plot_model(finalModel,'re', sort.est ="(Intercept)", 
          colors= c(1,1))
```

\newpage

## Plots

```{r eval=F}
gx = plot_model(finalModel, 'eff', vars=c("matcherResponds.cumulative"), 
               title = '', prnt.plot = F,
               show.ci=T, facet.grid = F)

pdf("../../results/graphs/CumulativeMatcherTurns.pdf",
    width=4,height=4)
gx$matcherResponds.cumulative + 
  xlab("Number of previous trials where\nmatcher responded") + 
  ylab("Probability of correct choice") + 
  #scale_x_continuous(breaks = c(0,5,10,15)) + 
  coord_cartesian(xlim=c(0,15)) 
dev.off()
```

```{r eval=F, echo=F}
plot_model(finalModel, 'eff',show.ci=T, facet.grid = F)
```

## Variance explained

Total variance explained by the model: Calculated by pseudo R squared method from the *MuMIn* package to calculate the variance explained by fixed effects and random effects in a model (Nakagawa & Schielzeth 2013). 

```{r message=F,warning=F}
r.squaredGLMM.binom = function(object){
fam <- family(object)
  fitted <- (model.matrix(object) %*% MuMIn:::.numfixef(object))[,1L]
  varFE <- var(fitted)
  mmRE <- MuMIn:::.remodmat(object)
  vc <- MuMIn:::.varcorr(object)
  varRE <- MuMIn:::.varRESum(vc, mmRE)
  familyName <- fam$family
  null <- MuMIn:::.nullFitRE(object)
  fixefnull <- unname(MuMIn:::.numfixef(null))
  vt <- MuMIn:::.varRESum(MuMIn:::.varcorr(null), mmRE)
  pmean <- fam$linkinv(fixefnull - 0.5 * vt * tanh(fixefnull * 
                                    (1 + 2 * exp(-0.5 * vt))/6))
  MuMIn:::r2glmm(fam, varFE, varRE, pmean = pmean)
}
```


```{r message=F,warning=F}
r.squaredGLMM.binom(finalModel)
fee = r.squaredGLMM.binom(finalModel)[1,1]
tee = r.squaredGLMM.binom(finalModel)[1,2]
ree = tee-fee
```

Fixed effects explain `r signif(fee,4)*100`% of the variance. Total varaince explained = `r signif(tee,4)*100`%. (random effects = `r signif(ree,4)*100`).

For each model in the bottom-up procedure, we then calculate the increase in variance explained. This is an estiamte of how much variance a particular variable accounts for.

```{r message=F,warning=F}
mList = list("m0"=m0,"con"=con,"mod"=mod,"modXcon"=modXcon,
  "game"=game,"trialL"=trialL,"trialLXmo"=trialLXmo,
  "t1L"=t1L,"t1LXmo"=t1LXmo,"mtchTrn"=mtchTrn,"tMtchTr"=tMtchTr,
  "tMaTXmo"=tMaTXmo,"multi"=multi,"block"=block)
mList = mList[rownames(modelComparison)]
varExplained = sapply(mList,r.squaredGLMM.binom)
varExplained.fixed = diff(varExplained[1,])

t(t(varExplained.fixed[c("mod","con","modXcon",
                     "game","trialL","mtchTrn")]))
```


## Summary results

```{r}
signif(finalRes[,c("Estimate","Std. Error","z value",
                   "Pr(>|z|)",'Chisq',"Pr(>Chisq)")],2)
```

