---
title: "Modality effects in a signalling game"
output: pdf_document
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), "../../results/MainResults_Efficiency.pdf")) })
---

# Intro 

The main data used in this analysis comes from `../../data/FinalSignalData.csv` (compiled by  `analyseData.R`).  Each row represents one signal, but this script only keeps one signal per trial, and the rest of the analysis is on the trial-by-trial level.  The variables in the data are as follows (some are calculated in the script below):

-  X: ID
-  filename: Filename of the ELAN file
-  dyadNumber: ID of the participant dyad
-  condition: Stimuli type (Auditory or Visual)
-  game: Game number (0-3)
-  trial: Trial number (0-15)
-  target: Target stimuli shown to the director
-  choice: Meaning chosen by the matcher
-  correct: True if the matcher's choice is correct
-  trialStart, trialEnd, trialLength: Start, end and length of trial in milliseconds
-  trialValue:  A unique string that represents data from the trial.  Numbers in the curly brackets represent the choices given to the matcher
-  startOfNextTrial: Timestamp for next trial, used in processing the data.
-  turnStart, turnEnd, turnLength: the start, end and length of the turn in milliseconds.
-  signalStart, signalEnd, signalLength: the start, end and length of the signal.
-  signalType:  Annotation value in ELAN, not meaningful
-  tiralString: Unique string to identify trial
-  modalityCondition:  The condition for the dyad (multi= multimodal, visual=gesture only, vocal=vocal only)
-  playerId:  Unique ID for the participant producing the signal 
-  itemId:  Unique ID for the target stimulus
-  turnString:  Unque ID for the turn
-  matcherResponds:  Does matcher take a turn in this trial?
-  matcherResponds.cumulative: The (scaled) number of previous trials that a has responded.
-  T1Length, T1Length.log:  Length and log length of the director's first turn.
-  trialTotal: Number of trials played so far, scaled (and centered) to represent number of games played.
-  firstBlock:  Block order
-  incorrect:  Was the matcher's choice incorrect?
-  multimodal:  Was the director's first turn multimodal?


## Load libraries

```{r warning=FALSE, message=FALSE}
library(lme4)
library(sjPlot)
library(ggplot2)
library(lattice)
library(influence.ME)
library(dplyr)
```

```{r echo=F}
try(setwd("~/Documents/MPI/ViniciusMultimodal/multimodalCommunicationGame/experiment/analysis/R/"))
```

## Load data

```{r}
d = read.csv("../../data/FinalSignalData.csv")
```

Variable for length of first T1

```{r}
T1L = tapply(d[d$turnType=="T1",]$turnLength,
             d[d$turnType=="T1",]$trialString, head, n=1)
d$T1Length = T1L[d$trialString]
d$T1Length[is.na(d$T1Length)] = mean(d$T1Length,na.rm=T)
d$T1Length.log = log(d$T1Length)
d$T1Length.log = d$T1Length.log - mean(d$T1Length.log)
```

We don't need info on every signal in each turn, just the trial time.  Keep only 1st signal in each trial.

```{r}
d = d[!duplicated(d$trialString),]
```


# Descriptive stats

Make a variable to represent proportion of games played:

```{r}
# Make a variable that represents the number of trials played
d$trialTotal = d$trial + (d$game * (max(d$trial)+1))
# Convert to proportion of games played, so that estimates reflect change per game.
d$trialTotal = d$trialTotal / 16
```

Here is a graph showing the distribution of trial lengths by conditions:

```{r}
summary = d %>% 
  group_by(condition, modalityCondition,game) %>% 
  summarise(Efficiency=mean(trialLength),
            sd=sd(trialLength),
            ci.w =           qnorm(0.95)*sd/sqrt(length(trialLength)),
            upper=Efficiency+ci.w,
            lower = Efficiency-ci.w)
summary$game = summary$game +1

summary$modalityCondition =
  factor(summary$modalityCondition,
         levels = c("visual",'multi','vocal'),
         labels=c("Gestural","Multimodal","Vocal"))

ggplot(d, aes(x=trialTotal, y=trialLength,colour=modalityCondition)) +
  geom_smooth() + facet_grid(.~condition)

ggplot(d, aes(x=trialTotal, y=trialLength,colour=condition)) +
  geom_smooth() + facet_grid(.~modalityCondition)

gx1 = ggplot(summary, aes(x=game, y=Efficiency, group=condition, colour=modalityCondition)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=0.5) +
  facet_grid(. ~ condition) +
  stat_summary(fun.y="mean", geom="line", aes(group=modalityCondition)) +
    geom_point() +
  scale_colour_discrete(name="Condition") +
  ggtitle("Efficiency") +
  xlab("Game") +
  ylab("Trial length (ms)")

gx1
pdf("../../results/graphs/Efficiency_gg.pdf",
    width = 5, height=3)
gx1
dev.off()

gx2 = ggplot(summary, aes(x=game, y=Efficiency, group=condition, colour=condition, shape=condition)) + 
  geom_errorbar(aes(ymin=lower, ymax=upper), width=0.5) +
  facet_grid(. ~ modalityCondition) +
  stat_summary(fun.y="mean", geom="line", aes(group=condition)) +
    geom_point() +
  scale_colour_discrete(name="Stimuli") +
  scale_shape_discrete(name="Stimuli") +
  xlab("Game")

gx2
pdf("../../results/graphs/Efficiency_gg_alt.pdf",
    width = 5, height=3)
gx2
dev.off()
```

![The efficiency of trials in different conditions](../../results/graphs/Efficiency.pdf)

Average trial time for the whole experiment:

```{r}
mean(d$trialLength)
sd(d$trialLength)
```



The distribution of trial times is very skewed:

```{r}
hist(d$trialLength)
```

So we transform it using a log transform, then center the data.

```{r}
d$trialLength.log = log(d$trialLength)
meanLogTrialLength = mean(d$trialLength.log)
d$trialLength.log = d$trialLength.log - meanLogTrialLength 
hist(d$trialLength.log)
```

```{r}
# Center the trialTotal variable so intercept reflects after the first game
d$trialTotal = d$trialTotal - 2

matcherResponds.cumulative.mean = mean(d$matcherResponds.cumulative)

d$matcherResponds.cumulative = d$matcherResponds.cumulative - matcherResponds.cumulative.mean

d$matcherResponds = factor(d$matcherResponds)

```

Make a variable for which stimuli the players experienced first.

```{r}
firstBlock = tapply(as.character(d$condition),d$dyadNumber,head,n=1)
d$firstBlock = as.factor(firstBlock[match(d$dyadNumber,names(firstBlock))])
```


Reorder some levels so that the intercept reflects the most frequent condition.

```{r}
d$incorrect = !d$correct
```

Variable for whether T1 was a multimodal signal.

```{r}

turnD = read.csv("../../data/Final_Turn_data.csv")
turnD = turnD[turnD$turnType=="T1",]
turnD = turnD[turnD$role == "Director",]
d$multimodal = turnD[match(d$trialString, turnD$trialString),]$turnModalityType == "multi"
d$multimodal[is.na(d$multimodal)] = F

```



\newpage

# Mixed models

Make a series of models with random effects for dyad, director (nested within dyad) and item.

Not all random slopes are appropriate.  For example, items are used in only one stimulus condition, so a random slope for condition by item is not appropriate.  Similarly, each dyad only plays in one modality condition.

It is reasonable to have a random slope for trial by dyad, but this caused unreliable model convergence, so is not included.

The final random slopes were for condition and incorrectness by dyad/player, and modality condition by item.

```{r models, cache=TRUE}
# No fixed effects
m0 =  lmer(trialLength.log ~ 1 + 
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

```

Now we add a series of possible confounding factors such as whether the matcher responds.  We add the main experimental factors at the end to ensure that they're really contributing to the model over and above the confounds.

```{r models2, cache=FALSE}
# Add number of matcher turns
mtchTrn = lmer(trialLength.log ~ 1 +
                matcherResponds +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

tMtchTr = lmer(trialLength.log ~ 1 +
                matcherResponds +
                matcherResponds.cumulative +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add whether the response was incorrect
incor = lmer(trialLength.log ~ 1 + 
            matcherResponds + 
            matcherResponds.cumulative +  
            incorrect +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
```


```{r models3, cache=TRUE}


# Add multimodal signal

multim = lmer(trialLength.log ~ 1 + 
            matcherResponds +
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add effect of trial

game = lmer(trialLength.log ~ 1 + 
            trialTotal + 
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add the quadratic effect of trial
gamQuad = lmer(trialLength.log ~ 1 + 
            trialTotal + I(trialTotal^2) +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
```


```{r models5, cache=T}
# Add modality condition
modality =  lmer(trialLength.log ~ 1 + modalityCondition + 
            trialTotal + I(trialTotal^2) +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
# Add stimulus condition
cond = lmer(trialLength.log ~ 1 + modalityCondition + condition + 
            trialTotal + I(trialTotal^2) +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add interaction between modality and stimulus condition
modXcond = lmer(trialLength.log ~ 1 + modalityCondition*condition +
           trialTotal + I(trialTotal^2) +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
```

```{r models6, cache=T}
# Add interaction between condition and trial
conXgame = lmer(trialLength.log ~ 1 + modalityCondition*condition +
            trialTotal + I(trialTotal^2) +
              condition:trialTotal +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
# Add interaction between modality and trial
modXgame = lmer(trialLength.log ~ 1 + modalityCondition*condition +
             trialTotal + I(trialTotal^2) +
              condition:trialTotal + modalityCondition:trialTotal +
            matcherResponds + 
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add 3-way interaction
moXcoXga =  lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
```

Interactions

```{r models8, cache=T}
# interaction between turns and modality
nTurnXmo = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds + matcherResponds:modalityCondition +
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

nTurnXco = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds + matcherResponds:modalityCondition +
            matcherResponds:condition +
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Turn x modality x condtion
# Note that the acousitc modality had hardly any matcher turns, 
# so the factor is dropped

tuXmoXco = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
            incorrect + 
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add the interaction between modality and incorrectness
moXincor =   lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
            incorrect + incorrect:modalityCondition +
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
# Add the interaction between condition and incorrectness
coXincor =  lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
            incorrect + incorrect:modalityCondition + incorrect:condition +
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
# Add the three-way interaction between condition, modality and incorrectness
coXmoXin = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
            incorrect *modalityCondition*condition +
            multimodal +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

```


```{r models4, cache=TRUE}
# Interaction between multimodality and condition
multiXco = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
            incorrect *modalityCondition*condition +
            multimodal + multimodal:condition + 
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)

# Add interaction between quadratic effect of trial and modality
modXgamQ =  lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +(modalityCondition:I(trialTotal^2)) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative +
            incorrect *modalityCondition*condition +
            multimodal + multimodal:condition + 
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)



```


Interactions with matcher turns

```{r models 3.5, cache=TRUE}
tMaTxMod = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +(modalityCondition:I(trialTotal^2)) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
              matcherResponds.cumulative:modalityCondition +
            incorrect *modalityCondition*condition +
            multimodal + multimodal:condition + 
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = FALSE)
```

Check block has no effect

```{r}
# Add block order
block =  lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +(modalityCondition:I(trialTotal^2)) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
              matcherResponds.cumulative:modalityCondition +
            incorrect *modalityCondition*condition +
            multimodal + multimodal:condition + 
            matcherResponds +
            firstBlock +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = TRUE)# Last model is REML to get estimates

# Add interaction between block order and modality
blocXmod = lmer(trialLength.log ~ 1 + modalityCondition*condition*trialTotal +
             I(trialTotal^2) +(modalityCondition:I(trialTotal^2)) +
            matcherResponds*modalityCondition*condition +
            matcherResponds.cumulative + 
              matcherResponds.cumulative:modalityCondition +
            incorrect *modalityCondition*condition +
            multimodal + multimodal:condition + 
            matcherResponds +
            firstBlock*modalityCondition +
            (1 + condition + incorrect |dyadNumber/playerId) + 
            (1 + modalityCondition|itemId),
          data=d, REML = TRUE)   
```


\newpage

# Results

Compare the fit of the models:

```{r anova}
modelComparison = anova(m0,modality,cond,game,modXcond,conXgame, modXgame,
      moXcoXga,mtchTrn,tMtchTr,tMaTxMod,nTurnXmo,nTurnXco,tuXmoXco,
      incor,moXincor,coXincor,coXmoXin,
      multim,multiXco,
      gamQuad,modXgamQ,
      block, blocXmod)
attributes(modelComparison)$heading = ""
modelComparison
```

Pick final model for estimates:

```{r}
finalModel = block
```

Final model estimates:

```{r}
summary(finalModel)
```


Check model predictions.  The model predictions are in the right range and direction, fitting linear quite well:

```{r}
plot(predict(blocXmod),d$trialLength.log, pch=16, col=rgb(0,0,0,0.4),
     ylim=c(-1.5,2),xlim=c(-1.5,2))
abline(a=0,b=1, col=2, lwd=2)
abline(h=0, col=2)
abline(v=0, col=2)

cor(predict(finalModel), d$trialLength.log)
```

The residuals are ok, though it tends to do worse at higher values.  This is expected from using the log scale.

```{r}
qqnorm(resid(blocXmod))
qqline(resid(blocXmod))
```


## Plot the fixed effects

Relabel the effects:

```{r}

feLabels = matrix(c(
"(Intercept)"             ,"Intercept"      , NA,                         
"modalityConditionvisual" ,"Visual modality", "modality",
"modalityConditionvocal"  , "Acoustic modality", "modality",
"conditionVisual" , "Visual stimuli","cond",
"trialTotal"             , "Game","game",
"modalityConditionvisual:conditionVisual"  , "Visual modality:Visual stimuli", "modXcond",
"modalityConditionvocal:conditionVisual" , "Acoustic modality:Visual stimuli","modXcond",
"modalityConditionvisual:trialTotal"    , "Visual modality:Game","modXgame",
"modalityConditionvocal:trialTotal"     , "Acoustic modality:Game", "modXgame",
"conditionVisual:trialTotal"             , "Visual stimuli:Game","conXgame",
"modalityConditionvisual:conditionVisual:trialTotal", "Visual modality:Visual stimuli:Game", "moXcoXga",
"modalityConditionvocal:conditionVisual:trialTotal", "Acoustic modality:Visual stimuli:Game", "moXcoXga",
"incorrectTRUE","Incorrect","incor",
"modalityConditionvisual:incorrectTRUE","Visual modality:Incorrect","moXincor",
"modalityConditionvocal:incorrectTRUE","Acoustic modality:Incorrect","moXincor",
"modalityConditionvisual:I(trialTotal^2)", "Visual modality:Game^2","modXgamQ",
"modalityConditionvocal:I(trialTotal^2)", "Acoustic modality:Game^2","modXgamQ",
"I(trialTotal^2)","Game^2","gamQuad",
"firstBlockVisual","Visual stims first","block",
"modalityConditionvisual:firstBlockVisual","Visual modality:Visual stim first","blocXmod",
"modalityConditionvocal:firstBlockVisual","Acoustic modality:Visual stim first","blocXmod",
"conditionVisual:incorrectTRUE","Visual stimuli:incorrect","coXincor",
"modalityConditionvisual:conditionVisual:incorrectTRUE","Visual modality:Visual stimuli:incorrect","coXmoXin",
"modalityConditionvocal:conditionVisual:incorrectTRUE","Acoustic modality:Visual stimuli:incorrect","coXmoXin",

"modalityConditionvisual:conditionVisual:numberOfTurns","VisualModality:Visual stim:NumTurns","tuXmoXco",
"modalityConditionvisual:conditionVisual:matcherRespondsTRUE","VisualModality:Visual stim:Matcher Responds","tuXmoXco",
"modalityConditionvocal:conditionVisual:numberOfTurns","Vocal Modality:Visual stim:NumTurns","tuXmoXco",
"modalityConditionvocal:conditionVisual:matcherRespondsTRUE","Vocal Modality:Visual stim:Matcher Responds","tuXmoXco",
"conditionVisual:numberOfTurns","Visual stim:NumTurns","nTurnXco",
"conditionVisual:matcherRespondsTRUE","Visual stim:Matcher Responds","nTurnXco",
"modalityConditionvisual:numberOfTurns","VisualModality:NumTurns","nTurnXmo",
"modalityConditionvisual:matcherRespondsTRUE","VisualModality:Matcher Responds","nTurnXmo",
"modalityConditionvocal:numberOfTurns","Vocal Modality:NumTurns","nTurnXmo",
"modalityConditionvocal:matcherRespondsTRUE","Vocal Modality:Matcher Responds","nTurnXmo",
"numberOfTurns","Number of turns","nTurns",
"multimodalTRUE","Multimodal T1","multim",
"conditionVisual:multimodalTRUE","VisualStim:MultimodalT1","multiXco",
"matcherRespondsTRUE","Matcher Responds",'mtchTrn',
"matcherResponds.cumulative","Total interaction","tMtchTr",
"modalityConditionvisual:matcherResponds.cumulative","Total interaction:Visual Modality","tMaTxMod",
"modalityConditionvocal:matcherResponds.cumulative","Total interaction:Vocal Modality","tMaTxMod"
), ncol=3, byrow = T)

feLabels2 = as.vector(feLabels[match(names(fixef(finalModel)),feLabels[,1]),2])
feModel = as.vector(feLabels[match(names(fixef(finalModel)),feLabels[,1]),3])

sig = modelComparison$`Pr(>Chisq)`
names(sig) = rownames(modelComparison)

sig.data = data.frame(estimate = fixef(finalModel),
                      y=1:length(fixef(finalModel)),
                      sig=sig[feModel])

cols= c("black",'red')
sig.data$pointCol = cols[1]
sig.data$pointCol[!is.na(sig.data$sig)] = 
  cols[1 + (sig.data$sig[!is.na(sig.data$sig)] < 0.05)]
# Mark marginal effects
#sig.data$pointCol[!is.na(sig.data$sig) & 
#                    sig.data$sig < 0.1 & 
#                    sig.data$sig >=0.05] = "orange"
  
sig.data$fade = sig.data$sig > 0.05
```

Plot the strength of the fixed effects:

```{r fixEf, warning=F}
x = sjp.lmer(finalModel, 'fe', 
         show.intercept = T,
         sort.est=NULL,
         axis.labels = feLabels2[2:length(feLabels2)],
         xlab="Trial time (log ms)",
         geom.colors = c(1,1),
         show.p=F,
         show.values = F,
         p.kr = FALSE,
         string.interc="Intercept",
         prnt.plot = F) 

x$plot.list[[1]]$data$fade = sig.data$fade

x$plot.list[[1]] 
```

\newpage

Attempt plot with axes in milliseconds.

```{r fixEfMilliseconds, warning=F}
convertEst = function(X){
  exp(meanLogTrialLength+X) - exp(meanLogTrialLength)
}

x$plot.list[[1]]$data$estimate =convertEst(x$plot.list[[1]]$data$estimate)
x$plot.list[[1]]$data$conf.low = convertEst(x$plot.list[[1]]$data$conf.low)
x$plot.list[[1]]$data$conf.high =  convertEst(x$plot.list[[1]]$data$conf.high)

sig.data2 = sig.data
sig.data2$estimate = x$plot.list[[1]]$data$estimate
sig.data2$estimate.lower = x$plot.list[[1]]$data$conf.low
sig.data2$estimate.upper = x$plot.list[[1]]$data$conf.high

x$plot.list[[1]]$data$fade = sig.data2$fade

x$plot.list[[1]] + 
  scale_y_continuous(name="Difference (ms)") +
  scale_x_discrete(labels=feLabels2) + 
  #geom_point(data=sig.data2,aes(y=estimate,x=y,fade=fade), color=sig.data$pointCol) +
  coord_flip(ylim=c(-5000,10000))
  

```

for every 10 trials where a matcher responded, subsequent trials were shorter by:

```{r}

noInteraction = convertEst(
  fixef(finalModel)["(Intercept)"]
)

tenResponses = convertEst(
  fixef(finalModel)["(Intercept)"] +
  (10 * fixef(finalModel)["matcherResponds.cumulative"])
)

noInteraction - tenResponses
```


\newpage

Table for paper

```{r}
outdata = x$plot.list[[1]]$data[,c("estimate","conf.low",'conf.high')]

outdata$estimate = round(outdata$estimate)
outdata$conf.low = round(outdata$conf.low)
outdata$conf.high = round(outdata$conf.high)
#outdata = outdata[2:nrow(outdata),]

xd = as.data.frame(summary(finalModel)$coef)
#xd = xd[2:nrow(xd),]
outdata$wald.t = xd$`t value`

sig = modelComparison$`Pr(>Chisq)`
names(sig) = rownames(modelComparison)
sigx = sig[feModel]
#sigx = sigx[2:length(sigx)]

outdata$model.comparison.p = sigx
outdata$estimate = paste(
  c("","+")[1+(outdata$estimate>0)],
  as.character(outdata$estimate),sep='')

outdata$label = feLabels2

outdata = outdata[,c("label","estimate","conf.low",
                     "conf.high","wald.t",
                     "model.comparison.p")]

write.csv(outdata[2:nrow(outdata),],file="../../results/tables/Efficiency_FixedEffects.csv")
```


## Random effects

There is a reasonable amount of variaition in the random effects, suggesting that dyads and players differ.  This justifies the use of mixed effects modelling.

```{r ranEf}
dotplot(ranef(finalModel))
```

qq-plots of random effects

```{r ranEfQQ}
sjp.lmer(finalModel, type = "re.qq")
```


## Relevel factors to see other comparisons

```{r}
d2 = d
d2$condition = relevel(d2$condition,"Visual")
fm2 = update(finalModel, data=d2)
summary(fm2)

feLabelsB = feLabels2
feLabelsB = gsub("Visual stimuli","Acoustic stimuli",feLabelsB)
feLabelsB = gsub("VisualStim","AcousticStim",feLabelsB)
feLabelsB = gsub("Visual stim","AcousticStim",feLabelsB)

x2 = sjp.lmer(fm2, 'fe', 
         show.intercept = T,
         sort.est=NULL,
         axis.labels = feLabelsB[2:length(feLabelsB)],
         xlab="Trial time (log ms)",
         geom.colors = c(1,1),
         show.p=F,
         show.values = F,
         p.kr = FALSE,
         string.interc="Intercept",
         prnt.plot = F) 

x2$plot.list[[1]]$data$fade = sig.data$fade

x2$plot.list[[1]] 

```



```{r}
d2 = d
d2$modalityCondition = relevel(d2$modalityCondition,"visual")
fm2 = update(finalModel, data=d2)
summary(fm2)

feLabelsB = feLabels2
feLabelsB = gsub("Visual modality","Multimodal",feLabelsB)


x2 = sjp.lmer(fm2, 'fe', 
         show.intercept = T,
         sort.est=NULL,
         axis.labels = feLabelsB[2:length(feLabelsB)],
         xlab="Trial time (log ms)",
         geom.colors = c(1,1),
         show.p=F,
         show.values = F,
         p.kr = FALSE,
         string.interc="Intercept",
         prnt.plot = F) 

x2$plot.list[[1]]$data$fade = sig.data$fade

x2$plot.list[[1]] 

```


# More plots

```{r eval=F}
x = sjp.lmer(tMtchTr,'eff', 'matcherResponds.cumulative', show.ci = T, prnt.plot = F)$plot 
```

```{r eval=F}
x$data$y = exp(x$data$y + meanLogTrialLength)
x$data$ci.low = exp(x$data$lower + meanLogTrialLength)
x$data$ci.high = exp(x$data$upper + meanLogTrialLength)
x$data$x = x$data$x + matcherResponds.cumulative.mean

x$labels$title = NULL

pdf("../../results/graphs/CumulativeMatcherTurns_Efficiency.pdf",
    width=4,height=4)
x + #xlim(0,10) + 
  geom_ribbon(aes(ymin=ci.low,ymax=ci.high),alpha = 0.15) + 
  scale_x_continuous(limits=c(0,15)) + 
  scale_y_continuous(breaks = c(0,3000,6000,9000,12000)) +
  #coord_cartesian(xlim = c(5, 10))  +
  xlab("Number of previous trials where\nmatcher responded") + 
  ylab("Trial time (ms)") + 
  theme(strip.background = element_blank(),
       strip.text.x = element_text(colour = 'white'))
dev.off()

```





